Binary companions of red giant stars with APOGEE: \\ catalog and companions that survive the common envelope

### 2017-12-15 paper/1-catalog/twoface-catalog.tex
intro stab

Nearly all stars form with stellar companions in multiplets or clusters, through
subsequent dynamical evolution that stars may lose their neighbors.
Main sequence stars in the solar neighborhood more often appear in binary or
multiple star systems than singles (\citealt{ragavhan,tokovinin,todo}).
- Related to fragmentation in collapsing protostellar / molecular cloud ->
  multiple stars (e.g., \citealt{Raskutti:2016})
- Population of stellar binaries and multiplets -> information about star
  formation, dynamics

Even without stellar or sub-stellar companions, single stars likely have
planetary-mass companions (\citealt{todo}.
- Different formation channel for planets?
- Sub-stellar companions?

- Almost all stars have companions of some mass
These systems have a large dynamic range of constituent and orbital
characteristics.
For example, for binary main-sequence stars, mass-ratios span from XX to 1 and
periods from XX to YY years.
- Population of companions and trends (e.g., with metallicity) -> star and
  planet formation processes

- Expect differences in evolved star pop. from main sequence populations:
  - mass loss
  - envelope -> engulfment?
- But less is known about the population of companions to evolved stars.
- Current samples limited in dynamical range of chemical properties, location,
  age (local to sun)
- Brighter, but typically larger distances, direct imaging not feasible
- Eclipsing companions good, but low mass companions stars -> hard to find
  (giants are big)
- Need large sample of stars with time-domain spectroscopy

>>>>

Stars typically have companions.

Main sequence stars in the solar neighborhood more often appear in binary or
multiple star systems rather than as solitary stars
(\citealt{ragavhan,tokovinin,todo}).
This is likely a generic outcome of star formation: turbulent fragmentation in
collapsing protostellar clouds tends to produce multiplets of stars within
length-scales comparable to their spheres of influence (e.g.,
\citealt{Raskutti:2016}).
Binary and multiple star systems are therefore of great interest in
astrophysics: the population of stars and their companions encodes information
about star formation processes (\citealt{todo}), stellar parameters and
evolution (\citealt{todo}), and the dynamics of multi-body systems
(\citealt{todo}).

Even without stellar or sub-stellar companions, single stars likely have
planetary-mass companions (\citealt{todo}).
\todo{Planetary systems are interesting because...yadda yadda}
Differences between the population of stellar companions and that of
planetary-mass companions likely relate directly to the different formation
channels for these objects.

\todo{should we name ``stars with companions'' something like ``stellar
systems''?}
Stars with companions have a large dynamic range of constituent and orbital
characteristics.
For example, for binary main sequence stars, mass-ratios span from XX to 1 and
periods from XX to YY years.
For planetary companions of main sequence stars, \todo{}.
- Some indication of trends (e.g., with metallicity) -> star and
  planet formation processes

Most of what is known about stellar companions comes from main sequence stars.
- Some evolved stars have special roles in exotic systems like cataclysmic
  variables (donor stars)
- But less is known about the population of companions to evolved stars.
- Expect differences in evolved star pop. from main sequence populations:
  - mass loss
  - envelope -> engulfment?
- Current samples limited in dynamical range of chemical properties, location,
  age (local to sun)
- Brighter, but typically larger distances, direct imaging not feasible
- Eclipsing companions good, but low mass companions stars -> hard to find
  (giants are big)
- Need large sample of stars with time-domain spectroscopy
